Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-27 methods_paper/fabl-paper.tex
update.

Consider ordered record pairs $\bm{X}_1 \times \bm{X}_2.$ 
Denote the set of matches by $\bm{M} = \{(i,j): i \in \bm{X}_1, j \in \bm{X}_2, \Delta_{ij} = 1\}.$ Denote the set of non-matches 
$\bm{U} =  \{(i,j): i \in \bm{X}_1, j \in \bm{X}_2, \Delta_{ij} = 0\}.$ An alternative way of merging two databases and removing 
duplications can be viewed as identifying the sets of matches/non-matches, or rather $\bm{M}, \bm{U}.$ In the literature, it is well known that record pairs that are estimated as matches are known as links; record pairs that are estimated as non-matches are known as non-links. \cite{fellegi_theory_1969} proposed using all-to-all pairwise comparison of records to estimate the matches/non-matches.

@@

@@

>>>>

Consider ordered record pairs $\bm{X}_1 \times \bm{X}_2,$ where the size of the databases are $n_1$ and $n_2,$ respectively. 
Denote the set of matches by $\bm{M} = \{(i,j): i \in \bm{X}_1, j \in \bm{X}_2, \Delta_{ij} = 1\}.$ Denote the set of non-matches 
$\bm{U} =  \{(i,j): i \in \bm{X}_1, j \in \bm{X}_2, \Delta_{ij} = 0\}.$ An alternative way of merging two databases and removing 
duplications can be viewed as identifying the sets of matches/non-matches, or rather $\bm{M}, \bm{U}.$ In the literature, it is well known that record pairs that are estimated as matches are known as links; record pairs that are estimated as non-matches are known as non-links. \cite{fellegi_theory_1969} proposed using all-to-all pairwise comparison of records to estimate the matches/non-matches.

@@

\subsection{Blocking}
In practice, it is not feasible to make all-to-all record comparisons as the computationally complexity is of the order $O(n_1 \times n_2).$ The most common solution is utilize blocking, which places similar records into partitions, clusters, or ``blocks" to reduces this computational burden. Blocking can be deterministic, such as reducing the dimensionality of the comparison space on a highly reliable feature, such a gender. Blocking can be probabilistic, such as utilizing machine learning methods, known as hashing, which seek to use probabilistic functions (with low computational cost) to place similar records into the same bin. We propose hashing base methods for Bayesian bipartite record linkage, illustrating their ability to improve upon computational scalability. We emphasize that depending on the size of the problem, our proposed methodology can be used with or without hashing.

@@

\textcolor{red}{Brian: The Gibbs sampler has some minor typos. It should be written in terms of $\bm{Z}, \Phi, \lambda \mid \gamma_{obs}.$ Also, just make the rest of the notation match please:)}
